---
title: "Creating Parsimonious Model"
author: "Michael Harper"
date: '`r format(Sys.Date())`'
output: github_document
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE, tidy.opts=list(width.cutoff=60))

source(file = "../Functions.R") # Load Functions

# Load Data from Preprocessing
TurbineData <- read.csv("../01-Data/Preprocessed/TurbineDataset.csv")

```

So far, the model has only removed variables if they were deemed to be erroneous: primarily this was checked through the diagnostic checks which looked for collinear variables and autocorrelation. However the significance of the parameters has so far been ignored. 

The aim of this section is remove parameters from the fifth model while minimizing the reduction in the Pseudo $R^{2}$ values. In doing so, it aims to produce a simplified model which contains only the most important parameters while maintaining the level of predictive ability of the model.

The following parameters were remaining in the model after the hierarchical analysis filtered datasets which violated the logistic assumptions:

```{r}

# Extract parameters into a dataframe
VariableList <-  c("No..of.Turbines","Turbine.Capacity..MW.","Windspeed45","Ukelevation","Powerlines","Airports","Aroads","Broads","Minroads","Motorways","Railway","Urbanregions","Aonb","Nationalparks","Hcoast","Nnr","Ramsar","Sacs","Spa","Sssi","Qual_PercentL4","Age_Mean","PercentOwner","SocialGradePercentAB","Con_share","Lab_share","LD_share") 

```

## Model Reduction

The building of the model was based on the logical classification of parameters based on their inferred importance in decision making. In order to optimise the model, it seemed appropriate that a step-wise model was used to remove the least significant parameters.

```{r}

WindModel <- LogisticModel(VariableList, TurbineData)

# List Least Importance parameters
importance <- round(caret::varImp(WindModel), 3)
(importanceordered <- importance[order(importance$Overall), 1,  drop=FALSE])

# Number of parameters to exclude from best GLM
Remove <- 13

```

The worst performing variables will be prefiltered from the optimisation to improve computation time. For $n$ parameters removed, there will be a computational speed increases of $2^n$. The parameters removed are: `r row.names(importanceordered)[1:Remove] ` 

## Finding the Best Fitting Model

The "bestglm" package is used to find the best fitting subset of parameters. 

```{r}

# Filter variable list by removing lowest x parameters
VariableList <- ParameterUpdate(VariableList, remove = c(row.names(importanceordered)[1:Remove]))

# Full data must be formatted in suitable way for analysis
colref <- match(VariableList, names(TurbineData))
datasubset <- TurbineData[ ,c(colref, 66)]

# Identify best fit
BestglmResults <- bestglm::bestglm(datasubset, IC="AIC",family = binomial)

# Save the results for the best model
BestModel <- BestglmResults$BestModel

# Show summary statistics
summary(BestModel)
```

**********

# Reporting Best Model

Typical diagnostics are done for the model to assess the performance

```{r}

LogisticDiagnostics(BestModel)

```

Plotting odds graphs. Although there is a function to do this, it has been altered to be included within a publication.

```{r}

LogOddsPlotGraphCustom <- function(ModelDF, Sort = FALSE){
  # Produces boxplots for estimated values from a regression model
  #
  # Args:
  #   ModelDF: a formatted odds table from the function "LogisticOddsTable"
  #   PlotTitle: the title of the resulting plot
  #   plotColour: the output colour of the boxplots
  #   Sort: reorder the plot by variable fit
  #
  
  # Rename Variables
  ModelDF$term <- matchNames(ModelDF$term)
  Terms <- ModelDF$term
  suppressWarnings(library(ggplot2))
  
  # Determine Max vales for axes
  Ymax <- 1.4
  Ymin <- 0.6
  
  offset = 1 # Defines where barplots start from
  linebreak = 0.1
  MixedColour <- "skyblue3"
  Negative <- "red1"
  Positive <- "palegreen"
  windowsFonts(Times=windowsFont("TT Times New Roman")) # Load correct font
  
  # --- Plot Graph
  plotlogodds <- ggplot(ModelDF, aes(x = term, y = odds - offset, fill = Relationship, width = 0.8)) +
    # Plots Data
    geom_bar(position=position_dodge(), stat="identity", colour = "black", size = 0.5) +
    geom_errorbar(aes(ymin = ci_lower - offset, ymax = ci_upper - offset),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9),
                  size = 0.4,
                  colour = "grey20"
    ) +
    # Axes
    labs(y = "Odds Ratio") +
    scale_y_continuous(labels = seq( from = Ymin, to =  Ymax, by = linebreak),
                       breaks = seq(from = Ymin - offset, to = Ymax - offset, by = linebreak),
                       limits = c(Ymin, Ymax) - offset,
                       expand=c(0,0)
    ) +
    scale_x_discrete(limits = rev(Terms)) +
    scale_fill_manual(values = c("Mixed" = MixedColour, "Negative" = Negative, "Positive" = Positive)) + 
    geom_hline(yintercept = 0) +
    # Theme
    theme(plot.title = element_text(hjust = 0.5),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major = element_line(colour = "grey46",  size = 0.2),
          axis.title.y=element_blank(),
          panel.background = element_rect(fill = "white", colour = "grey46"),
          axis.ticks = element_line(colour = "grey46",  size = 0.2),
          text = element_text(family="Times", size=12, colour = "black"),
          axis.text = element_text(family="Times", size=11, colour = "black"),
          panel.spacing = unit(c(0,0,0,0), units = "cm")
    ) +
    coord_flip()
  
  return(plotlogodds)
}

# CHange legend title to confidence interval

# Combine Custom Function with other Logistic Odds Table Function
LogisticOddsPlotCustom <- function(Model, Sort = FALSE){
  a <- LogisticOddsTable(Model, Sort)
  b <- LogOddsPlotGraphCustom(a)
  return(b)
}

# Plot Table
(OddsPlot <- LogisticOddsPlotCustom(BestModel, Sort = FALSE))

```

# Save Plot for Journal

```{r SavePlot, message=FALSE, warning="hide"}

jpeg(filename = "ReducedVariables_OddsPlot.jpg", width = 17, height = 6, units = "cm", res = 600)
OddsPlot
dev.off()

```

# Odds Table

```{r Odds Table}

LogisticTableRename <- function(Model){
  # Combines the logistic results table function with the function
  # to rename variables to their full name
  # Args:
  #   Model: a logistic regression model
  #
  LogisticModel <- LogisticResultsTable(Model)
  LogisticModel[,1] <- matchNames(LogisticModel[,1])
  return(LogisticModel)
}

# Produce and Save Results
(BestModelResults <- LogisticTableRename(BestModel))

write.csv(x = BestModelResults, file = "ReducedVariables_ResultsTable.csv", row.names = FALSE)

```

# Model Accuracy

```{r}

ReducedParameterList <- c("No..of.Turbines", "Urbanregions", "Nationalparks", "Ramsar", "Spa", "Qual_PercentL4", "Age_Mean", "Lab_share", "LD_share")

ModelAccuracy(TurbineData, "Status.Summary", ReducedParameterList)


```



