---
title: "Data Preprocessing"
author: "Michael Harper"
date: '`r format(Sys.Date())`'
output:  github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Data

The turbine data is laoded into the file. This contains a number of variables:

```{r}

TurbineData <- read.csv("Input/FullInfo_AllTurbines.csv")
names(TurbineData)

```

## Data Transformation

Planning status has been summarised to three variables:

1) Accepted
2) In Planning (Decision Pending)
3) Rejected

For simplification, any turbines still in planning were removed:

```{r}

# Removes "Awaiting Decision" Factor from list
TurbineData <- data.frame(TurbineData[TurbineData$Status.Summary != "Submitted", ])

# Relevel data to make the Reject 0 and Accept 1 
TurbineData$Status.Summary <- factor(TurbineData$Status.Summary) # relevel factor
TurbineData$Status.Summary <- relevel(TurbineData$Status.Summary, "Refused/Abandoned") 

# Add a numeric ID for planning status.
TurbineData$Planning_Status_Code <- TurbineData$Status.Summary  %in% "Approved"
TurbineData$Planning_Status_Code <- TurbineData$Planning_Status_Code * 1 # Convert TRUE FALSE to 1 and 0

```

## Filtering Smaller Turbines

Finally, the analysis only deals with large wind turbines (projects which are greater than 1MW in capacity). The smaller turbines are therefore filtered from the database:

```{r}

TurbineData <- TurbineData[TurbineData$Size == "Large", ]

```

The resulting dataset has a total of `r nrow(TurbineData)` observations.

## Saving Data

The resulting dataset is saved as a CSV to be used within the following stages of the analysis.

```{r}

write.csv(x = TurbineData, file = "Preprocessed/TurbineDataset.csv")

```


